Cosmological constraints from the redshift dependence of the Alcock-Paczynski effect: constraining the linear evolution of dark energy

### 2017-07-13 Draft/Draft0.8.tex
minor changes

\author{ 
Xiao-Dong Li,$^{1}$
Cristiano G. Sabiu,$^{2}$
Changbom Park,$^{1}$
Yuting Wang,$^{3}$
Gong-bo Zhao,$^{3}$
Hyunbae Park,$^{2}$
Arman Shafieloo,$^{2}$
Juhan Kim,$^{4,1}$
and Sungwook E. Hong$^{2}$}

  \affiliation{School of Physics, Korea Institute for Advanced Study, 85 Heogi-ro, Dongdaemun-gu, Seoul 130-722, Korea}
  \affiliation{Korea Astronomy and Space Science Institute, 776, Daedeokdae-ro, Yuseong-gu, Daejeon, 305-348, Korea}
  \affiliation{National Astronomy Observatories, Chinese Academy of Science, Beijing, 100012, P.R.China}
  \affiliation{Center for Advanced Computation, Korea Institute for Advanced Study, 85 Hoegi-ro, Dongdaemun-gu, Seoul 130-722, Korea}

\begin{abstract}
We use the small scale anisotropic clustering signal of 1,133,326 galaxies from the Sloan Digital Sky Survey Data Release 
12, spanning the redshift range $0.15<z<0.69$ to place constraints on the expansion history of the Universe. 
Concentrating on the Chevallier-Polarski-Linder parametrization of dark energy, $w=w_0+w_a\frac{z}{1+z}$,
while improving upon earlier works \citep{Li2016}, 
we present a novel use of the Alcock-Paczynski (AP) test via the small scales clustering difference between redshift bins. 
This differential measure is shown to be a robust statistical tool that mitigates many systematic effects, 
allowing for competitive and unbiased constrains to be placed on cosmological parameters.
We find that our results, in combination with the CMB, BAO, SNIa and $H_0$ from Cepheid data yield, 
$\Omega_m = 0.301 \pm 0.008,\ w_0 = -1.042 \pm 0.067,\ w_a = -0.07 \pm 0.29$ (68.3\% CL). 
Addint our new AP measurements to the aforementioned results 
reduces the error bars by 30-40\%,
and reduces the area of $w_0-w_a$ contour by 50\%.
The AP method can be combined with the standard BAO method,
greatly increasing the power of ongoing and future galaxy surveys in probing dark energy.
\end{abstract}

@@

In recent years the Alcock-Paczynski (AP) test \citep{AP1979} applied to galaxy redshift samples \citep{Outram2004,Blake2011,Alam2016}, 
has allowed tight constraints to be placed on the background averaged distance scales, $D_A(z)$ and $H^{-1}(z)$.  
Assuming an incorrect cosmological model for the coordinate transformation between redshift space and comoving space, produces residual geometric distortions in the resultant galaxy distribution. 
These distortions are induced by the fact that measured distances along 
and perpendicular to the line of sight are fundamentally different. 
Measuring the ratio of galaxy clustering in the radial and transverse directions provides a probe of this AP effect.

@@

The main caveat in applying the AP test is due to the fact that 
the radial distances of galaxies are inferred from observed redshifts.
Thus AP tests are inevitably affected by peculiar the motions of galaxies,
which leads to apparent anisotropy in the clustering signal, even if the adopted cosmology is correct.
The effect, known as redshift-space distortions (RSD),
is notoriously difficult to model accurately in the statistics of galaxy clustering \citep{Ballinger1996}.

@@

In an earlier work\citep{Li2016} we applied this AP method to galaxies from the 3rd incarnation of the Sloan Digital Sky Survey (SDSS-III). 
Combining the method with measurements of the Cosmic Microwave Background (CMB), type Ia supernovae (SNIa), 
baryon acoustic oscillations (BAO), and $H_0$,
we obtained very tight constraints of $ \Omega_m = 0.301 \pm 0.006,\ w=-1.054 \pm 0.025$.
In reducing the RSD effect, 
we were able to use galaxy clustering on scales down to 6 $h^{-1}$Mpc,
which is a major advance in extracting cosmological information 
on small scales where galaxy clustering is strong and there are many independent structures.

@@

The CPL parametrization has many obvious advantages, for instance, a manageable parameter space, 
the bounded behavior at high redshift, 
and the ability to accurately reconstruct many dark energy theories\cite{CPL_L}. 
So it was widely used in the literature to reconstruct dark energy from observations.
Fig.\ref{fig_xy} shows that redshift dependence of shape distortion is sensitive to both $w_0$ and $w_a$.
So we expect these two parameters effectively constrained by our method.

@@

In detail, the number of pairs are only counted in a fiducial cosmology
-- which is taken as the $\Omega_m=0.26$ $\Lambda$CDM --
and ``translated'' to the measurements in a ``target'' cosmology using the relations, 
\begin{eqnarray}
 s_{\rm target} = s_{\rm fiducial} \sqrt{\alpha_{\parallel}^2 \mu_{\rm fiducial}+\alpha_{\bot}(1-\mu_{\rm fiducial}^2)}, \\
 \mu_{\rm target} = \mu_{\rm fiducial} \frac{\alpha_\parallel}
 {\sqrt{\alpha_{\parallel}^2 \mu_{\rm fiducial} +\alpha_{\bot}(1-\mu_{\rm fiducial}^2)}}
\end{eqnarray}
where $\alpha_{\bot}\equiv D_{A,\rm target}/D_{A,\rm fiducial}$,
$\alpha_{\parallel}\equiv H_{\rm fiducial}/H_{\rm target}$.
and values of $D_A$ and $H$ are computed in the effective redshifts of the six redshift bins.
In the fiducial cosmology
we measure $\xi(s,\mu)$ in an ultra high resolution of
$\Delta s = 0.2 {\rm Mpc/h}$, $\Delta \mu = 1/600$,
%Let us call this ``approximate 2pCF'' method.
%to obtain the accurate number counts 
and these small ``pixels'' are grouped to infer 
the number counts in other cosmologies, 
in large pixels of $\Delta s = 1 {\rm Mpc/h}$, $\Delta \mu = 1/120$.
%in the fiducial cosmology and group the bins in the target cosmology.
In the case when one small pixel belongs to more than one larger pixel,
a correction is applied by computing the fraction of the overlapping area.

@@

\begin{figure*}
   \centering{
   \includegraphics[width=16cm,natwidth=6,natheight=5]{fig_con_tests.pdf}
   %\includegraphics[width=9cm,natwidth=4,natheight=4]{fig2b.pdf}
   %\includegraphics[height=8cm]{fig2b.pdf}
%   \includegraphics[height=8cm]{Tpcf--plot--Normed.eps}
%    \includegraphics[height=8cm]{smu.eps}
   }
   \caption{\label{fig_contest}
   Robustness test of the results.
   For the ``default'' constraints (pink contours) are derived using six redshift bins, 
   $\mu_{\rm max}=0.97$, $n_{\mu}=15-20$, $s=6-40 \rm Mpc/h$,
   a fiducial cosmology $\Omega_m=0.26,\ w=-1.0$ for the measurement of 2pCF,
   systematic effects estimated from HR4 simulations, 
   and covariance estimated using 2,000 PATCHY mocks.
   When altering these options, the results remain robust (black contours).
   }
\end{figure*}

The Planck team has released the {\texttt {COSMOMC}} \citep{LB2002} outputs of four MCMC ``chains'' in the CPL model, 
using a combination of four datasets:
the full-mission Planck observations of CMB temperature and polarization anisotropies \cite{Planck2015},
the BAO distance priors measured from SDSS DR11 \citep{Anderson2013}, 6dFGS \citep{6dFGS} and SDSS MGS \citep{MGS},
the ``JLA'' SNIa sample \citep{JLA},
and the Hubble Space Telescope measurement of $H_0=70.6\pm3.3$ \cite{Riess2011,E14H0}.
These MCMC chains contain the CMB+BAO+SNIa+$H_0$ likelihood computed for $\sim$37,000 sets of cosmological parameters,
yielding constraints of %$ \Omega_m = 0.309 \pm 0.010, w_0 = -0.938 \pm 0.109, w_a = -0.38 \pm 0.41$.
\begin{eqnarray}
 \Omega_m &=& 0.309 \pm 0.010,  \\ \nonumber
 w_0 &=& -0.938 \pm 0.109,  \\ \nonumber
 w_a &=& -0.38 \pm 0.41.
\end{eqnarray}
%To derive the constraints combined with our AP method,
%we then compute the likelihood of the SDSS LOWZ+CMASS AP measurements for each of the parameter combinations provided in the Planck chain. 
%To do this, we splited the 1,133,326 galaxies from the SDSS DR12 into six redshift bins,
%measured the 2pCF (on scales of 6-40 $h^{-1}$Mpc) in these redshift bins (see Fig.\ref{fig_nbar}).
%This enables us investigating the redshift evolution of anisotropic clustering.
%We subtracted the systematic effects based on estimations from mocks made from Horizon Run 4 simulations \citep{HR4},
%and used a $\chi^2$ function to assess the redshift dependence.
%(see Methods for further explanations).
After adding the log-likelihoods of the Planck team sample with ours, 
while also multiply the sample weights by our likelihoods, 
we derive the CMB+BAO+SNIa+$H_0$+AP constraints on CPL parameters, %$\Omega_m = 0.301 \pm 0.008, w_0 = -1.042 \pm 0.067, w_a = -0.07 \pm 0.29$.
\begin{eqnarray}
\Omega_m &=& 0.301 \pm 0.008, \\ \nonumber
w_0 &=& -1.042 \pm 0.067, \\ \nonumber
w_a &=& -0.07 \pm 0.29.
\end{eqnarray}
While the central values of parameters do not shift appreciably,
the error bars of $w_0$ and $w_a$ are reduced by 38.4\% and 29.7\%, respectively.% $$-40\%$ by adding our method into the analysis.

The marginalised constraints on $w_0-w_a$ are shown in the left panel of Fig.\ref{fig_con}.
Adding our new AP constraints significantly reduces the allowable parameter space. 
This can also be visualise as allowable bands in $w(z)$ as can be seen in the right panel of Fig.\ref{fig_con}.

The derived cosmological constraints are fully consistent with a cosmological constant dark energy component having no evolution.
Adding the new AP method to the CMB+BAO+SNIa+$H_0$ constraints reduces the statistical errors on many parameters by $\sim$30-40\% 
and reduces the $w_0-w_a$ (95.4\% CL) contour by 50\%.
This reveals the constraining power of the small scale AP effect for probing the redshift evolution of dark energy.

We performed a thorough test of all the possible variables in our methodology.
Figure \ref{fig_contest} shows that 
the result is unaffected by the line-of-sight $\mu$-cut, 
the number of angular bins, 
the range of radial integration and the choice of fiducial cosmology. 
%we adopt $\mu_{\rm max}=0.99\ (0.85)$ to include more (less) regions near the LOS,
%decrease the number of angular bins to $n_{\mu}=15-20$,
%change the range of clustering to $8-30 \rm Mpc/h$,
%change the fiducial cosmology to $\Omega_m=0.26,\ w=-0.6$,
%exclude 1 or 2 high redshift bins,
%or reduce the number of mocks to 1000.
The most striking point to note in our testing is that the 
shift in contour position is very small even when we do not include the systematic correction.
This is reassuring, since we may have worried that {\it cosmological dependence} 
of the systematic correction could influence the final result.

@@

In summary, we previously proposed to constrain cosmological parameters via 
the redshift dependence of anisotropic galaxy clustering\cite{Li2016}.
This approach enables a robust AP test on relatively small scales.
In this paper we improved the methodology and obtained tight constraints on the CPL parametrization of dark energy.
%using 1,133,326 galaxies from the Sloan Digital Sky Survey Data Release 
%12 spanning the redshift range $0.15<z<0.69$ . 
%Adding our constraints to the CMB+SNIa+BAO+$H_0$ combination, the $w_0-w_a$ contour was reduced by $\sim50$\%.

@@

The presented method of clustering shells can be applied to many spectroscopic galaxy surveys. 
The method is complimentary to the BAO method and the two methods can be combined together, 
increasing (by roughly twice) the power of ongoing and future surveys, with little to no additional cost.
We expect this approach will play an important role in helping us unveiling the mystery of dark energy.

>>>>

\author{ 
Xiao-Dong Li,$^{1}$
Cristiano G. Sabiu,$^{2}$
Changbom Park,$^{1}$
Yuting Wang,$^{3}$
Gong-bo Zhao,$^{3}$
Hyunbae Park,$^{2}$
Arman Shafieloo,$^{2}$
Juhan Kim,$^{4}$
and Sungwook E. Hong$^{2}$}

  \affiliation{School of Physics, Korea Institute for Advanced Study, 85 Heogi-ro, Dongdaemun-gu, Seoul 02455, Korea}
  \affiliation{Korea Astronomy and Space Science Institute, 776, Daedeokdae-ro, Yuseong-gu, Daejeon, 34055, Korea}
  \affiliation{National Astronomy Observatories, Chinese Academy of Science, Beijing, 100012, P.R.China}
  \affiliation{Center for Advanced Computation, Korea Institute for Advanced Study, 85 Hoegi-ro, Dongdaemun-gu, Seoul 02455, Korea}

\begin{abstract}
We use the small scale anisotropic clustering signal of 1,133,326 galaxies from the Sloan Digital Sky Survey Data Release 
12, spanning the redshift range $0.15<z<0.69$ to place constraints on the expansion history of the Universe. 
Concentrating on the Chevallier-Polarski-Linder parametrization of dark energy, $w=w_0+w_a\frac{z}{1+z}$,
while improving upon earlier works \citep{Li2016}, 
we present a novel use of the Alcock-Paczynski (AP) test via the small scales clustering difference between redshift bins. 
This differential measure is shown to be a robust statistical tool that mitigates many systematic effects, 
allowing for competitive and unbiased constrains to be placed on cosmological parameters.
We find that our results, in combination with the CMB, BAO, SNIa and $H_0$ from Cepheid data yield, 
$\Omega_m = 0.301 \pm 0.008,\ w_0 = -1.042 \pm 0.067,\ w_a = -0.07 \pm 0.29$ (68.3\% CL). 
Adding our new AP measurements to the aforementioned results 
reduces the error bars by $\sim$30-40\%,
and reduces the area of $w_0-w_a$ contour by 50\%.
The AP method can be combined with the standard BAO method,
greatly increasing the power of ongoing and future galaxy surveys in probing dark energy, 
improving the figure of merit constraints on $(w_0,w_a)$ by a factor of 2. 
\end{abstract}

@@

In recent years the Alcock-Paczynski (AP) test \citep{AP1979} applied to galaxy redshift samples \citep{Outram2004,Blake2011,Alam2016}, 
has allowed tight constraints to be placed on the background averaged distance scales, $D_A(z)$ and $H^{-1}(z)$.  
Assuming an incorrect cosmological model for the coordinate transformation between redshift space and comoving space, produces residual geometric distortions in the resultant galaxy distribution, see  Fig.\ref{fig_xy}. 
These distortions are induced by the fact that measured distances along 
and perpendicular to the line of sight are fundamentally different. 
Measuring the ratio of galaxy clustering in the radial and transverse directions provides a probe of this AP effect.

@@

The main caveat in applying the AP test is that 
the radial distances of galaxies are inferred from observed redshifts.
Thus AP tests are inevitably affected by the peculiar motions of galaxies,
which leads to apparent anisotropy in the clustering signal, even if the adopted cosmology is correct.
The effect, known as redshift-space distortions (RSD),
is notoriously difficult to model accurately in the statistics of galaxy clustering \citep{Ballinger1996}.

@@

In an earlier work\citep{Li2016} we applied this AP method to galaxies from the 3rd incarnation of the Sloan Digital Sky Survey (SDSS-III). 
Combining the method with measurements of the Cosmic Microwave Background (CMB), type Ia supernovae (SNIa), 
baryon acoustic oscillations (BAO), and $H_0$,
we obtained very tight constraints of $ \Omega_m = 0.301 \pm 0.006,\ w=-1.054 \pm 0.025$.
In reducing the RSD effect, 
we were able to use galaxy clustering on scales down to 6 $h^{-1}$Mpc,
which is a major advance in extracting cosmological information 
on small scales where galaxy clustering is strong and many independent structures exist.

@@

The CPL parametrization has many obvious advantages, for instance, a manageable parameter space, 
the bounded behavior at high redshift, 
and the ability to accurately reconstruct many dark energy theories\cite{CPL_L}. 
So it was widely used in the literature to reconstruct dark energy from observations.
Especially, the DETF figure of merit (FoM) is defined the reciprocal of the area of the error
ellipse enclosing the 95\% confidence limit in the $w_0–w_a$ plane. 
This quantity quantifies the progress in measuring the properties of dark energy.
Larger FoM indicates greater accuracy.
Fig.\ref{fig_xy} shows that redshift dependence of shape distortion is sensitive to both $w_0$ and $w_a$.
So we expect these two parameters effectively constrained by our method.

@@

In detail, the number of pairs are only counted in a fiducial cosmology
-- which is taken as the $\Omega_m=0.26$ $\Lambda$CDM --
and ``translated'' to the measurements in a ``target'' cosmology using the relations, 
\begin{eqnarray}
 s_{\rm target} = s_{\rm fiducial} \sqrt{\alpha_{\parallel}^2 \mu_{\rm fiducial}+\alpha_{\bot}^2(1-\mu_{\rm fiducial}^2)}, \\
 \mu_{\rm target} = \mu_{\rm fiducial} \frac{\alpha_\parallel}
 {\sqrt{\alpha_{\parallel}^2 \mu_{\rm fiducial} +\alpha_{\bot}^2(1-\mu_{\rm fiducial}^2)}}
\end{eqnarray}
where $\alpha_{\bot}\equiv D_{A,\rm target}/D_{A,\rm fiducial}$,
$\alpha_{\parallel}\equiv H_{\rm fiducial}/H_{\rm target}$.
and values of $D_A$ and $H$ are computed in the effective redshifts of the six redshift bins.
In the fiducial cosmology
we measure $\xi(s,\mu)$ in an ultra high resolution of
$\Delta s = 0.2 {\rm Mpc/h}$, $\Delta \mu = 1/600$,
%Let us call this ``approximate 2pCF'' method.
%to obtain the accurate number counts 
and these small ``pixels'' are grouped to infer 
the number counts in other cosmologies, 
in large pixels of $\Delta s = 1 {\rm Mpc/h}$, $\Delta \mu = 1/120$.
%in the fiducial cosmology and group the bins in the target cosmology.
In the case when one small pixel belongs to more than one larger pixel,
a correction is applied by computing the fraction of the overlapping area.

@@

\begin{figure*}
   \centering{
   \includegraphics[width=16cm,natwidth=6,natheight=5]{fig_con_tests.pdf}
   %\includegraphics[width=9cm,natwidth=4,natheight=4]{fig2b.pdf}
   %\includegraphics[height=8cm]{fig2b.pdf}
%   \includegraphics[height=8cm]{Tpcf--plot--Normed.eps}
%    \includegraphics[height=8cm]{smu.eps}
   }
   \caption{\label{fig_contest}
   Robustness test of the results.
   For the ``default'' constraints (pink contours) are derived using six redshift bins, 
   $\mu_{\rm max}=0.97$, $n_{\mu}=15-20$, $s=6-40 \rm Mpc/h$,
   a fiducial cosmology $\Omega_m=0.26,\ w=-1.0$ for the measurement of 2pCF,
   systematic effects estimated from Horizon Run 4 simulations, 
   and covariance estimated using 2,000 MultiDark PATCHY mocks.
   When altering these options, the results remain robust (black contours).
   }
\end{figure*}

The Planck team has released the {\texttt {COSMOMC}} \citep{LB2002} outputs of four MCMC ``chains'' in the CPL model, 
using a combination of four datasets:
the full-mission Planck observations of CMB temperature and polarization anisotropies \cite{Planck2015},
the BAO distance priors measured from SDSS DR11 \citep{Anderson2013}, 6dFGS \citep{6dFGS} and SDSS MGS \citep{MGS},
the ``JLA'' SNIa sample \citep{JLA},
and the Hubble Space Telescope measurement of $H_0=70.6\pm3.3$ km/s/Mpc \cite{Riess2011,E14H0}.
These MCMC chains contain the CMB+BAO+SNIa+$H_0$ likelihood computed for $\sim$37,000 sets of cosmological parameters,
yielding constraints of %$ \Omega_m = 0.309 \pm 0.010, w_0 = -0.938 \pm 0.109, w_a = -0.38 \pm 0.41$.
\begin{eqnarray}
 \Omega_m &=& 0.309 \pm 0.010,  \\ \nonumber
 w_0 &=& -0.938 \pm 0.109,  \\ \nonumber
 w_a &=& -0.38 \pm 0.41.
\end{eqnarray}
%To derive the constraints combined with our AP method,
%we then compute the likelihood of the SDSS LOWZ+CMASS AP measurements for each of the parameter combinations provided in the Planck chain. 
%To do this, we splited the 1,133,326 galaxies from the SDSS DR12 into six redshift bins,
%measured the 2pCF (on scales of 6-40 $h^{-1}$Mpc) in these redshift bins (see Fig.\ref{fig_nbar}).
%This enables us investigating the redshift evolution of anisotropic clustering.
%We subtracted the systematic effects based on estimations from mocks made from Horizon Run 4 simulations \citep{HR4},
%and used a $\chi^2$ function to assess the redshift dependence.
%(see Methods for further explanations).
After adding the log-likelihoods of the Planck team sample with ours, 
while also multiply the sample weights by our likelihoods, 
we derive the CMB+BAO+SNIa+$H_0$+AP constraints on CPL parameters, %$\Omega_m = 0.301 \pm 0.008, w_0 = -1.042 \pm 0.067, w_a = -0.07 \pm 0.29$.
\begin{eqnarray}
\Omega_m &=& 0.301 \pm 0.008, \\ \nonumber
w_0 &=& -1.042 \pm 0.067, \\ \nonumber
w_a &=& -0.07 \pm 0.29.
\end{eqnarray}
While the central values of parameters do not shift appreciably,
the error bars of $w_0$ and $w_a$ are reduced by 38.4\% and 29.7\%, respectively.% $$-40\%$ by adding our method into the analysis.

The marginalised constraints on $w_0-w_a$ are shown in the left panel of Fig.\ref{fig_con}.
Adding our new AP constraints significantly reduces the allowable parameter space. 
This can also be visualised as allowable bands in $w(z)$ as can be seen in the right panel of Fig.\ref{fig_con}.

The derived cosmological constraints are fully consistent with a cosmological constant dark energy component having no evolution.
Adding the new AP method to the CMB+BAO+SNIa+$H_0$ constraints reduces the statistical errors on many parameters by $\sim$30-40\% 
and reduces the $w_0-w_a$ (95.4\% CL) contour by 50\%.
This constitutes a significant increase in the figure of merit (FoM)  constraints on $(w_0, w_a)$. This doubling of the FoM($w_o,w_a$) comes at no additional cost or alteration to survey design, thus greatly improving the overall cost-benefit consideration of large cosmological redshift surveys.

We performed a thorough test of all the possible variables in our methodology.
Fig.\ref{fig_contest} shows that 
the result is unaffected by the line-of-sight $\mu$-cut, 
the number of angular bins, 
the range of radial integration and the choice of fiducial cosmology. 
%we adopt $\mu_{\rm max}=0.99\ (0.85)$ to include more (less) regions near the LOS,
%decrease the number of angular bins to $n_{\mu}=15-20$,
%change the range of clustering to $8-30 \rm Mpc/h$,
%change the fiducial cosmology to $\Omega_m=0.26,\ w=-0.6$,
%exclude 1 or 2 high redshift bins,
%or reduce the number of mocks to 1000.
The most striking point to note in our testing is that the 
shift in contour position is very small even when we do not include the systematic correction.
This is reassuring, since we may have worried that {\it cosmological dependence} 
of the systematic correction could influence the final result.

@@

We previously proposed to constrain cosmological parameters via 
the redshift dependence of anisotropic galaxy clustering\cite{Li2016}.
This approach enables a robust AP test on relatively small scales.
In this paper we improved the methodology and obtained tight constraints on the CPL parametrization of dark energy.
%using 1,133,326 galaxies from the Sloan Digital Sky Survey Data Release 
%12 spanning the redshift range $0.15<z<0.69$ . 
%Adding our constraints to the CMB+SNIa+BAO+$H_0$ combination, the $w_0-w_a$ contour was reduced by $\sim50$\%.

@@

The presented method of clustering shells can be applied to many large spectroscopic galaxy surveys. 
We show that figure of merit constraints on  $(w_0, w_a)$ can be increased by a factor of 2 when considering the small scale clustering shells information in combination with existing constraints. The analysis we perform requires no change to the typical survey strategy of large cosmological redshift surveys, thus we can increasing (by roughly twice) the power of ongoing and future surveys, with little to no additional cost.
We expect this approach will play an important role in helping us unveiling the mystery of dark energy.
